Security vs. Maintainability: \\ Fixing Vulnerabilities Obfuscates your Code

### 2019-01-28 paper/ICPC19/icpc19.tex
acks
adding placehoder for t2v.

\section{Threats to Validity}\label{sec:threats}

\section{Related Work}\label{sec:rw}

@@

We thank to the Software Improvement Group (SIG) team for all the support and help in validating our methodology.

>>>>

\section{Threats to Validity}\label{sec:threats}
%
In this section, we discuss potential threats to the validity of our work.
%
\subsection{Construct}
%
We use a metric derived from the reports provided by BCH as a construct of
software maintainability. Different projects and contexts may require different
maintainability standards. However, BCH uses a representative benchmark of
closed and open source software systems to compute the thresholds used in each
maintainability guideline\cite{Visser:2016:OREILLY,baggen2012standardized}.
In addition, the benchmark is updated every year~\cite{Visser:2016:OREILLY}.

The lifespan of a given energy commit is an approximation based on a single
change in one of the lines of code submitted by that commit. Although changes in
whitespace are not considered, we did not perform any evaluation on the type of
change that is performed. Some changes may be trivial while others may have
required more efforts from developers. Related work has proposed approaches to
automatically classify changes (e.g., bug fixes\cite{da2017framework}, and
refactorings~\cite{pascarella2018self}), but we have not explored them.
Nevertheless, we understand that the differences in the lifespan between our
dataset of energy changes and the baseline provide interesting leads for
discussion and new research directions.

\subsection{Internal}

We resort to a set of security changes that were collected from previous
work~\cite{Reis:2017:IJSSE}. These dataset was collected using the commit
message provided by developers to classify a given commit as a security change.
We understand that this approach discards security changes that did not have an
explicit commit message describing them as such.

In the case of baseline commits, they were collected by randomly select a commit
in the same project that a given security change occurs. We use this approach to
control differences incurred by the specificities of each project. Still,
maintainability may be affected by different coding styles and experience level
from developers of the same project. We do not evaluate differences at that
level. Moreover, we do not evaluate the maintainbility difference for all
regular commits in a project. We assume that the size of the dataset is enough
to mitigate random variations in the maintainability differences of the baseline.

\subsection{External}

The dataset used in this work comprises code changes of free and open
source applications. Our methodology requires access to data that is not
publicly available for commercial apps. The extent to which this findings
generalize to commercial applications with non-open source licenses remains
a question to be answered in future work.

Moreover, all the security commits in this work are described in English.
%
\section{Related Work}\label{sec:rw}

@@

\noindent
We thank to the Software Improvement Group (SIG) team for all the support and
help in validating our methodology.
